%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Training Center Assistant} % Job title
    {Emergency Skills Inc.} % Organization
    {New York, NY} % Location
    {May 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted with the creation of training and promotional materials.}
        \item {Performed data entry and led collaborative initiatives involving proprietary client database.}
        \item {Scheduled training for existing and prospective clients.}
        \item {Coordinated meetings and scheduling for program manager.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Administrative Assistant, Town Clerk’s Office} % Job title
    {Town of Secaucus} % Organization
    {Secaucus, NJ} % Location
    {April 2018 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Processed and issued licenses and permits in accordance with State and local regulations.}
        \item {Corresponded with internal and external attorneys about Open Public Records Act compliance.}
        \item {Various clerical duties for the Clerk and Deputy Clerk.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Program Director, Drug Free Communities Grant} % Job title
    {} % Organization
    {} % Location
    {July 2017 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generated action plan in partnership with grant Program Coordinator.}
        \item {Budget management and planning for grant funds.}
        \begin{itemize}
          \item {Kept in accordance with grant spending requirements while adapting to community needs.}
          \item {Reported to federal monitor on spending and activities.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Administrative Assistant, Health Department} % Job title
    {} % Organization
    {} % Location
    {September 2016 - April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Processed and issued health licenses in accordance with State and local regulations.}
        \item {Prepared Board of Health Agendas for monthly open public meetings.}
        \item {Reconciled bank accounts for licensing fees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Keyboarding Clerk I, Town Clerk’s Office} % Job title
    {City of Cape May} % Organization
    {Cape May, NJ} % Location
    {May 2015 - September 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed records management (inventory and destruction) in accordance with State regulations.}
        \item {Processed and issued licenses in accordance with State and local regulations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Secretary, Shade Tree Commission} % Job title
    {} % Organization
    {} % Location
    {May 2015 - September 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared Agendas and Minutes for monthly open public meetings.}
        \item {Prepared reports on spending and activities for Town Council and Administration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Account Manager, Lower Township Municipal Utility Authority} % Job title
    {Environmental \& Technical Services} % Organization
    {Woodbine, NJ} % Location
    {May 2011 - May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed utility billing and collections for the township.}
        \begin{itemize}
          \item {Recorded payments from residents in corresponding utility account.}
          \item {Settled billing disputes between residents and the township.}
        \end{itemize}
        \item {Trained new employees on position procedures for various accounts.}
        \item {Entered water meter readings and metadata into billing software.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
